### 2012-02-22 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

@@

\todo[inline]{Dalsie pomocne funkcie a zaradit ich do nejakej kapitoly o pom. funkciach.}
\FORALL{$stepNode \in pathType.stepNodes$}
	\IF{$stepNode.isAxisStep()$}
		\STATE $axisKind = stepNode.getAxisNode().getAxisKind()$
		\IF{$axisKind$ $!=$ $CHILD$ $AND$ $axisKind$ $!=$ $DESCENDANT$}
			\RETURN false
		\ENDIF
	\ENDIF
\ENDFOR

>>>>

\subsection{Auxiliary Functions}
\todo[inline]{Dalsie pomocne funkcie a okomentovat.}
\todo[inline]{Algoritmu pouzivaju nejake nedefinovane funkcie, napr stepNode.getAxisNode().}

\FORALL{$stepNode \in pathType.stepNodes$}
	\IF{$stepNode.isAxisStep()$}
		\STATE $axisKind = stepNode.getAxisNode().getAxisKind()$
		\IF{$axisKind$ $!=$ $CHILD$ $AND$ $axisKind$ $!=$ $DESCENDANT$}
			\RETURN false
		\ENDIF
	\ENDIF
\ENDFOR

\begin{algorithm}
\caption{Function isWithoutPredicates}
\label{ALG_function_is_without_predicates}
\begin{algorithmic}[1]
\REQUIRE $pathType$: A $PathType$ instance.
\ENSURE A boolean result.

\FORALL{$stepNode \in pathType.stepNodes$}
	\IF{$stepNode.hasPredicates()$}
		\RETURN false
	\ENDIF
	\IF{$pathType.forBoundSubsteps[stepNode]$ $!=$ $null$}
		\IF{$isWithoutPredicates(pathType.forBoundSubsteps[stepNode]$ $==$ false}
			\RETURN false
		\ENDIF
	\ENDIF
\ENDFOR

\begin{algorithm}
\caption{Function endsWithExactlyOnePredicate}
\label{ALG_function_ends_with_exactly_one_predicate}
\begin{algorithmic}[1]
\REQUIRE $pathType$: A $PathType$ instance.
\ENSURE If $pathType$ ends with exactly one predicate, return value is the predicate, otherwise return value is false.

\STATE $lastStepNode =$ last item from $pathType.stepNodes$
\IF{$lastStepNode.hasPredicates()$ $==$ false}
	\RETURN false
\ENDIF
\IF{number of item in list $lastStepNode.getChild(PredicateListNode)$ $.getChildren()$ is higher than 1}
	\RETURN false
\ENDIF

\RETURN the only item in $lastStepNode.getChild(PredicateListNode)$ $.getChildren()$
\end{algorithmic}
\end{algorithm}

@@
